Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-01-08 vertical-thermal-review.Rmd
trying to replace buffering in wind speed sentence

Wind speeds are also higher at the top of the canopy, owing to the buffering effect of the canopy [@juckerCanopyStructureTopography2018].
This holds true across the range of forest types [Fig. `r fig_NEON_vertical`e, Supporting Information Figure `r SIfig_NEON_all`, @barnardSeasonalVariationCanopy2016a; @mcgregorTreeHeightLeaf2021; @juckerCanopyStructureTopography2018; @mullerEvidenceEfficientNonevaporative2021; @hanberryOpenForestEcosystems2020a; @hanberryReconceptualizationOpenOak2018] and savannas [@curtis_intracanopy_2019;@johnstonWhatLiesVertical2020]. 
Specifically, averaged across the NEON sites, maximum daily wind speeds were 4.1 m s^-1^ at the top of the vertical profile, compared to  $\le$ 1.1 m s^-1^ at the bottom of the vertical profile.
The implication is that upper canopy leaves have substantially higher boundary layer conductance ($g_b$) and therefore greater potential for both water and heat loss (see sections 2.2, 4.1).

>>>>

Wind speeds are also higher at the top of the canopy, that are substantially reduced moving into lower canopy layers due to resistance caused by canopy foliage  [@juckerCanopyStructureTopography2018; @jiao-junWindProfilesTrees2004].
This holds true across the range of forest types [Fig. `r fig_NEON_vertical`e, Supporting Information Figure `r SIfig_NEON_all`, @barnardSeasonalVariationCanopy2016a; @mcgregorTreeHeightLeaf2021; @juckerCanopyStructureTopography2018; @mullerEvidenceEfficientNonevaporative2021; @hanberryOpenForestEcosystems2020a; @hanberryReconceptualizationOpenOak2018] and savannas [@curtis_intracanopy_2019;@johnstonWhatLiesVertical2020]. 
Specifically, averaged across the NEON sites, maximum daily wind speeds were 4.1 m s^-1^ at the top of the vertical profile, compared to  $\le$ 1.1 m s^-1^ at the bottom of the vertical profile.
The implication is that upper canopy leaves have substantially higher boundary layer conductance ($g_b$) and therefore greater potential for both water and heat loss (see sections 2.2, 4.1).
